The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
perspectives intro

Our study is motivated by behavioural, landscape, and spatial ecology to build a
conceptual and analytical framework for scale-dependent multilayer networks and
we apply this framework to a case study of caribou (*Rangifer tarandus*) in
Newfoundland, Canada [@Peignier_2019]. We use this case study to address two
principal questions associated with scale-dependent multilayer networks. First,
to what degree does the social scale of relationships, spatial scale of
landscapes, and temporal scale of analysis influence our ability to interpret
complex social systems? Second, can variation in social, spatial, and temporal
improve predictions associated with biological differences in seasonal resource
availability and social association? We conclude with perspectives for further
development and application of scale in multilayer networks with respect to
landscape ecology (Schneider 2009)<!-- TODO-->, individual fitness and
phenotypes (Webber & Vander Wal 2018), and movement ecology and collective
movement (Jolles et al. 2019).

@@

# Perspectives  to advance multilayer networks 
## Habitat selection and space use

>>>>

Our study is motivated by behavioural, landscape, and spatial ecology to build a
conceptual and analytical framework for scale-dependent multilayer networks and
we apply this framework to a case study of caribou (*Rangifer tarandus*) in
Newfoundland, Canada [@Peignier_2019]. We use this case study to address two
principal questions associated with scale-dependent multilayer networks. First,
to what degree does the social scale of relationships, spatial scale of
landscapes, and temporal scale of analysis influence our ability to interpret
complex social systems? Second, can variation in social, spatial, and temporal
improve predictions associated with biological differences in seasonal resource
availability and social association? We conclude with perspectives for further
development and application of scale in multilayer networks with respect to
habitat selection and space use (REF)<!-- TODO-->, individual fitness and
phenotypes (Webber & Vander Wal 2018), and movement ecology and collective
movement (Jolles et al. 2019).

@@

# Perspectives  to advance multilayer networks

To date, behavioural ecology and social network researchers have made progress in describing the causes and consequences of the social environment in the context of (1) habitat selection and space use, (2) Individual fitness and phenotypes, and (3) movement ecology and collective movement. Here, we explore how mutlilayer networks may apply to these emerging fields to contribute to the development of spatial ecosystem ecology.

## Habitat selection and space use
